---
title: "Video Game Sales"
author: "Alayna Avila"
pagetitle: "Summer Project"
date: today

format:
  html:
    theme: cosmo
    toc: true
    toc-depth: 4
    toc-location: left
    embed-resources: true
    code-fold: false
    link-external-newwindow: true

execute:
  warning: false

from: markdown+emoji
reference-location: margin
citation-location: margin 
---

::: {.callout-tip icon=false}

## Github Repo Link

[Github Repo Link](https://github.com/amavila7/Video_Game_Analysis.git)

:::

## Overview

This is a summer project to showcase my skills. The goal is to explore a data set of interest, which in this case would be about video games since 1980's, as well as answer a few of my own research questions. I do some data tidying, a decent bit of exploratory data analysis, and finally, building predictive models. 

```{r}
#| label: libs
#| echo: false

library(tidyverse)
library(here)

games <- read_csv("data/games.csv")
```


# Data & Research Questions

## About the Data

The dataset is called `games.csv`and it is from Kaggle.^[] The data includes `50,000` video game records of the past 47 years of gaming history across 33 different platforms, 51 publishers, and 20 genres. It also includes regional sales, ratings, and some engineering columns. This is according to the Kaggle overview for this dataset. This dataset gets updated annually by Meruva Kodanda Suraj. He is a datasets expert with several badges, datasets, and competitions connected to his Kaggle account. 

## Quality Check

```{r}
#| label: miss-check
#| echo: false

naniar::miss_var_summary(games)
```



## Questions

### Inferential 

Do certain genres sell more than others?

```{r}

```



Do multiplayer games increase sales?

```{r}

```


How does microtransactions in a video game impact sales and launch price?

```{r}

```


### Prediction

What features or characteristics of a game are most likely to win Game of the Year?

Which traits of a video game go into defining the launch price of the video game?


# Procedure

# Analysis

**Do certain genres sell more than others?**

**Do multiplayer games increase sales?**

**How does microtransactions in a video game impact sales and launch price?**

**What features or characteristics of a game are most likely to win Game of the Year?**

**Which traits of a video game go into defining the launch price of the video game?**


## References

GeeksforGeeks. “Bootstrap Method.” GeeksforGeeks, July 23, 2025.  

[GeeksforGeeks](https://www.geeksforgeeks.org/maths/bootstrap-method/) was really helpful for conceptually understanding the bootstrap method. It provided clear mini examples of the process.
